---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# cleanR

<!-- badges: start -->
<!-- badges: end -->

The goal of cleanR is to provide some functionalists that can facilitate data cleaning.

## Installation

You can install the development version of cleanR from GitHub:

``` r
# install.packages("devtools")
remotes::install_github("axmedmaxamuud/cleanR")
```

## Examples

### Step 1: Create blank logbook

This is a basic example of creating a blank logbook that you can use it later to save the observation with issues. 

```{r, message=FALSE}
library(cleanR)

# create the logbook
my_logbook <- logbook()

# inspect the head of the logbook
head(my_logbook)

```


### Step 2: Log issues in the logbook

Now you can inspect the data and use the log_issue() to write the observations of the data that you find with the issues in the logbook. 

```{r}
check_age <- data %>% 
  filter(ki_age < 15) %>% 
  log_sheet(question.name = "ki_age",
            issue = "respondent is under 15 years old",
            action = "delete")
# inspect the check_age data
head(check_age)

```

now you can merge the check_age data with the logbook so you can maintain one logbook that can be exported at the end.

```{r}
my_logbook <- rbind(my_logbook, check_age)

head(my_logbook)
```


