---
title: "Cleaning food security indicators"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Cleaning_FSL_Indicators}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

In this article, we'll explore the crucial process of inspecting and cleaning food security indicators, following the guidelines of the WFP indicator compendium. We ensure data quality by using the cleanR package and Survey Designer, allowing us to understand the reasons behind certain results and take corrective actions during field data collection.

## Step 1: Load packages & data

```{r, echo=TRUE, warning=FALSE, message=FALSE, comment=FALSE}

# required packages
library(tidyverse)
library(cleanR)

# load raw data
moda_data <- cleanR::survey_data

```

## Step 2: Format data



## Step 3: Inspect quality of indicators



## Step 4: Generate summary reports




## Step 5: Export cleaning log file













