---
title: "Cleaning Food Security Indicators"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Cleaning_FSL_Indicators}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Welcome to the cleanR package documentation! This guide is designed to assist the WFP team in cleaning food security and livelihood data using the cleanR package. Our goal is to streamline the data cleaning process, ensuring consistency with the WFP Survey Designer for standardized variable naming.

## Step 1: Load packages & data

Start by uploading the raw data, typically the version downloaded from the MoDa server. Ensure that the data structure aligns with the WFP Survey Designer for consistent variable naming.

```{r, echo=TRUE, warning=FALSE, message=FALSE, comment=FALSE}
# required packages
library(tidyverse)
library(DT)
library(cleanR)

# load raw data
moda_data <- cleanR::survey_data %>% # converting HDDS variables to numeric
  mutate(across(starts_with("HDDS"), as.numeric))

```

## Step 2: Format data

The calculate_fsl_indicators function is a powerful tool for computing essential food security and livelihood (FSL) indicators, including the food consumption score, household dietary diversity, reduced coping strategy, and livelihood coping strategy, from your raw data.


```{r}
raw_data <- calculate_fsl_indicators(data = moda_data,
                                 # FCS
                                 FCSStap = "FCSStap", 
                                 FCSPulse = "FCSPulse", 
                                 FCSPr = "FCSPr", 
                                 FCSVeg = "FCSVeg", 
                                 FCSFruit = "FCSFruit",
                                 FCSDairy = "FCSDairy", 
                                 FCSFat = "FCSFat", 
                                 FCSSugar = "FCSSugar", 
                                 cutoff = "Cat28", 
                                 # rCSI
                                 rCSILessQlty = "rCSILessQlty", 
                                 rCSIBorrow = "rCSIBorrow", 
                                 rCSIMealSize = "rCSIMealSize", 
                                 rCSIMealAdult = "rCSIMealAdult", 
                                 rCSIMealNb = "rCSIMealNb",
                                 # HHS
                                 HHhSNoFood_FR = "HHhSNoFood_FR", 
                                 HHhSBedHung_FR = "HHhSBedHung_FR", 
                                 HHhSNotEat_FR = "HHhSNotEat_FR", 
                                 # HDDS
                                 # HDDSStapCer = "HDDSStapCer", 
                                 # HDDSStapRoot = "HDDSStapRoot", 
                                 # HDDSVeg = "HDDSVeg", 
                                 # HDDSFruit = "HDDSFruit", 
                                 # HDDSPrMeat = "HDDSPrMeat", 
                                 # HDDSPrEgg = "HDDSPrEgg", 
                                 # HDDSPrFish = "HDDSPrFish", 
                                 # HDDSPulse = "HDDSPulse", 
                                 # HDDSDairy = "HDDSDairy", 
                                 # HDDSFat = "HDDSFat", 
                                 # HDDSSugar = "HDDSSugar", 
                                 # HDDSCond = "HDDSCond"
                                 )


```

## Step 3: Use visualizations

By incorporating ridge charts into your analysis, you can easily identify patterns and variations in FCS and rCSI across different clusters or field monitors. 

```{r, warning=FALSE, fig.width=8, fig.height=5, message=FALSE}
(plot_ridge_distribution(raw_data, numeric_cols = c("FCSStap", "FCSPulse", "FCSPr", "FCSVeg", "FCSFruit", "FCSDairy", "FCSFat", "FCSSugar"),
                         name_groups = "Food Groups", name_units = "Days", grouping = "Area_Office"))

```

By carefully examining and interpreting the ridge chart, you can gain valuable insights into the distributions and flag any inconsistency for validation and review during data collection. in the below chart, we'll group the reduced coping strategies at area office level.


```{r, warning=FALSE, fig.width=8, fig.height=5, message=FALSE}
(plot_ridge_distribution(raw_data, numeric_cols = c("rCSILessQlty", "rCSIBorrow", "rCSIMealSize", "rCSIMealAdult", "rCSIMealNb"),
                         name_groups = "Food Coping Strategy", name_units = "Days", grouping = "Area_Office"))

```

similarly, you can group distributions at field monitor level to gain more insights at the consistency of reported distributions across different monitors. 

```{r, warning=FALSE, fig.width=8, fig.height=5, message=FALSE}
(plot_ridge_distribution(raw_data, numeric_cols = c("rCSILessQlty", "rCSIBorrow", "rCSIMealSize", "rCSIMealAdult", "rCSIMealNb"),
                         name_groups = "Food Coping Strategy", name_units = "Days", grouping = "EnumName"))

```


## Step 4: Generate cleaning log file

To facilitate collaboration and feedback collection, generate a cleaning log file. This log file will document flagged issues, providing insights into potential problems and capturing correct values for any identified inconsistencies.


```{r}
fsl_clog <- fsl_cleaning_log(data = raw_data, uuid = "uuid")

datatable(fsl_clog, list(dom = 't'))
```

Congratulations on successfully generating the cleaning log! To proceed, refer to the additional documentation for guidance on incorporating the corrected cleaning log file into the raw data to generate the clean dataset.



